---
title: "Linear Model with prediction 2"
author: "LuisJovelPalacios"
date: "2025-10-30"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(tigerstats)
require(knitr)

data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  
```

### Model1: SIMS-ARM

```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))
```


```{r}
basicNN + geom_point() + ggtitle("SIMS vs ARM") + theme(plot.title = element_text(hjust = 0.5, size = 20))
```

### Numerical Results

```{r}
cor(SIMS~ARM,data=data)
```


### Inferential Results 

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```

### Create target

```{r}
target <- data.frame(ARM=90,GRIP=90)
```

### Predict Target Point of model 1

```{r}
predict(model.1,target,interval =c("prediction"))
```

### Linear Fit Model1

```{r}
basicNN + geom_point () + ggtitle("SIMS-ARM") + theme(plot.title = element_text(hjust = 0.5, size = 20)) + geom_smooth(method = lm)
```

### Model 2 

```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=GRIP))
```

```{r}
basicNN + geom_point() +ggtitle("SIMS vs GRIP")+ theme(plot.title = element_text(hjust=0.5,size=20))
```

### Numerical Results

```{r}
cor(SIMS~GRIP,data=data)
```

### Inferential Results 

```{r}
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.2)
```

### Predict Target Point of model 2

```{r}
predict(model.2,target,interval =c("prediction"))
```

### Linear Fit Model2

```{r}
basicNN + geom_point () + ggtitle("SIMS-GRIP") + theme(plot.title = element_text(hjust = 0.5, size = 20)) + geom_smooth(method = lm)
```

### Model 3 SIMS~ARM+GRIP



### Numerical Results Model 3

```{r}
cor(SIMS~ARM+GRIP,data=data)
```

The correlation number for model 3 (SIMS~ARM+GRIP) is higher compared to model 2 (SIMS~GRIP) and model 1 (SIMS~ARM), so the correlation is better when using both models (ARM and GRIP) rather then using one of them (either ARM or GRIP)

### Inferential Results Model 3
```{r}
model.3 <- lm(SIMS~ARM+GRIP,data=data)
summary.lm(model.3)
```

The Formula for getting Model 3 is Formula = -5.433871 + 0.037311 * ARM + 0.024470 * GRIP

### Predict Target Point Of Model 3

```{r}
predict(model.1,target,interval =c("prediction"))
```

```{r}
predict(model.2,target,interval =c("prediction"))
```

```{r}
predict(model.3,target,interval =c("prediction"))
```


### Anova Test For Models

### Model1~Model3
```{r}
anova(model.1, model.3)
```

Our P-Value was 0.000004994 which is very small. Which tells us that model 3 is better than model 1 in a significant difference.

### Model2~Model3

```{r}
anova(model.2, model.3)
```

Our P-value for Model 2 and 3(0.00000001495) is even smaller than P-Value of model 1 and 3(0.000004994), which tells us that model 3 is the most accurate model of the 3 models.

### Model1~model2

```{r}
anova(model.1, model.2)
```

The sum of residual sum of square errors of model 2 is greater than model 1 which the difference of model 2 is -25.189.

### Discussion and Conclusion

In this assignment I learned to import the data from a given website. I was able to manipulate the data into 3 different models. The first model was SIMS~ARM, the second one was SIMS~GRIP, and the third one was SIMS~ARM+GRIP. I used a prediction code to estimate the values alongside scatterplots to visualize the lines of the best fir. I then used anova to compared all 3 models, and the analization in the end shoed me that model 3 has the best accuracy out of all the 3 models.
